Title

### 2013-03-27 inc/model_results/lens_charge/lens_charge.tex
tweaks for lens_charge section

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for oblate pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_long}) and a `short' focal length of 6.0mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_short}).
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
%A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\Fig \ref{fig:compare}).

>>>>

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for intially oblate ($ \xi ( 0 ) = 0.1 $) or prolate ($ \xi ( 0 ) = 10 $) pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm and a `short' focal length of 6.0mm.
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\ref{fig:compare_shape}).

### 2013-03-27 inc/model_results/lens_charge/lens_charge_plot.tex
tweaks for lens_charge section

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_long_oblate}
      \begin{tikzpicture}
        \input{lens_60mm_oblate_data}
        \node at (5.9,1.65) {$N=10^5$};
        \node at (4,3) {$N=10^6$};
        \node at (3,4) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] {
      \label{fig:focus_long_prolate}
      \begin{tikzpicture}
        \input{lens_60mm_prolate_data}
        \node at (4.2,2.3) {$N=10^5$};
        \node at (3.3,3.5) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \centerline{
    \subfloat[][] { 
      \label{fig:focus_short_oblate}
      \begin{tikzpicture}
        \input{lens_6mm_oblate_data}
        \node at (6.5,3) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] { 
      \label{fig:focus_short_prolate}
      \begin{tikzpicture}
        \input{lens_6mm_prolate_data}
        \node at (6.9,2.6) {$N=10^7$};
        \node at (6,2) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    All plot's pulses begin at the lens' front focal plane at 20 kV velocity ($c/3$) and have the same volume.
    The left plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_short_oblate}) are oblate shaped, initially HW1/eM width $ 500 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 0.1 $.
    The right plots (\subref{fig:focus_long_prolate} and \subref{fig:focus_short_prolate}) are prolate shaped, initially HW1/eM width $ 107.7 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 10 $.
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth.
    The top plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_long_prolate}) have a longer focal length $f = $ 60mm compared to the bottom plots (\subref{fig:focus_short_oblate} and \subref{fig:focus_short_prolate}) $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
    Clearly the best performance is achieved for shorter focal lengths and oblate pulses even at higher initial charge densities.
  }
  \label{fig:focus_lens_charge}
\end{figure}

>>>>

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_long_oblate}
      \begin{tikzpicture}
        \input{lens_60mm_oblate_data}
        \node at (5.9,1.65) {$N=10^5$};
        \node at (4,3) {$N=10^6$};
        \node at (3,4) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] {
      \label{fig:focus_long_prolate}
      \begin{tikzpicture}
        \input{lens_60mm_prolate_data}
        \node at (4.2,2.3) {$N=10^5$};
        \node at (3.3,3.5) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \centerline{
    \subfloat[][] { 
      \label{fig:focus_short_oblate}
      \begin{tikzpicture}
        \input{lens_6mm_oblate_data}
        \node at (6.5,3) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] { 
      \label{fig:focus_short_prolate}
      \begin{tikzpicture}
        \input{lens_6mm_prolate_data}
        \node at (6.9,2.6) {$N=10^7$};
        \node at (6,2) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    All plot's pulses begin at the lens' front focal plane at 20 kV velocity ($c/3$) and have the same volume.
    The left plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_short_oblate}) are initially oblate shaped, HW1/eM width $ 500 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 0.1 $.
    The right plots (\subref{fig:focus_long_prolate} and \subref{fig:focus_short_prolate}) are initially prolate shaped, HW1/eM width $ 107.7 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 10 $.
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth.
    The top plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_long_prolate}) have a longer focal length $f = $ 60mm compared to the bottom plots (\subref{fig:focus_short_oblate} and \subref{fig:focus_short_prolate}) $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
    Clearly the best performance is achieved for shorter focal lengths and oblate pulses even at higher initial charge densities.
  }
  \label{fig:focus_lens_charge}
\end{figure}
